Automatic Code Cleaning in R with `Rclean`

### 2020-03-12 ropensci/rclean_technote.Rmd
Edits technote adds install info

---
title: Rclean and Automatng Code Cleaning in R
author: M.K. Lau
bibliography: refs.bib
---

@@

@@

## Software Availability and Installation

Thanks to the efforts and helpful feedback from the ROpenSci
Community, the package has recently passed software review and we have
also recently published an article in the Journal of Statistical
Software. The package is hosted through the ROpenSci organization on
Github, and we recommend using the `devtools` library [@R-devtools] to
install directly from the repository (https://github.com/ROpenSci/Rclean).

>>>>

---
title: Automatic Code Cleaning in R with `Rclean`
author: M.K. Lau
bibliography: refs.bib
---

@@

# Installation

Through the helpful feedback from the ROpenSci community, the package
has recently passed software review and a supporting article was
recently published in the Journal of Open Source Software [@Lau2020],
in which you can find more details about the package. The package is
hosted through the ROpenSci organization on Github, and the package
can be installed using the `devtools` library [@R-devtools] directly
from the repository (https://github.com/ROpenSci/Rclean).

@@
